Estimating associations between childhood exposure to non-persistent endocrine disruptors, corticosteroids, and neurodevelopment: A study based on the parametric g-formula

### 2023-12-15 output/paper/_figures.qmd
Merged tables and figures for marginal effects into forest plots.

@@

```{r marginal-1}
#| label: fig-marginal-1
#| fig-cap: Average comparisons
#| fig-width: 6
#| fig-height: 7

tidy_res_meffects(
  df = marginal_comparisons_1,
  sa_var = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```

```{r marginal-2}
#| label: fig-marginal-2
#| fig-cap: Average comparisons
#| fig-width: 9
#| fig-height: 10

tidy_res_meffects(
  df = marginal_comparisons_2,
  sa_var = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```

```{r marginal-3}
#| label: fig-marginal-3
#| fig-cap: Average comparisons
#| fig-width: 5
#| fig-height: 5

tidy_res_meffects(
  df = marginal_comparisons_3,
  sa_var = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```

>>>>

```{r}
# Function to align forest plot with table numerical results
forest_plot <- function(obj, r = 4) {
  # From table of numerical results to ggplot object
  tbl_num_res <- obj$numerical_results |>
    tidylog::mutate(
      variable = forcats::fct_reorder2(
        variable, estimate, class
      )
    ) |>
    tidylog::select(-estimate) |>
    ggplot2::ggplot(
      ggplot2::aes(y = variable)
    ) +
    ggplot2::geom_text(
      ggplot2::aes(
        x = 0,
        label = variable
      ),
      hjust = 0,
      fontface = "bold"
    ) +
    ggplot2::geom_text(
      ggplot2::aes(
        x = 1,
        label = val
      ),
      hjust = 0,
      fontface = ifelse(
        obj$numerical_results$val == "Marginal contrast (95% CI)",
        "bold", "plain"
      )
    ) +
    ggplot2::theme_void() +
    ggplot2::theme(
      strip.background = ggplot2::element_blank(),
      strip.text = ggplot2::element_blank()
    ) +
    ggplot2::coord_cartesian(
      xlim = c(0, 4)
    )

  # Assemble elements
  ret <- patchwork::wrap_plots(
    tbl_num_res, obj$plot
  ) +
    patchwork::plot_layout(
      design = c(
        patchwork::area(t = 0, l = 1, b = 3, r = r),
        patchwork::area(t = 1, l = r, b = 3, r = r + 4)
      )
    )

  return(ret)
} # End function forest_plot
```

@@

```{r marginal-1}
#| label: fig-marginal-1
#| fig-cap: Marginal comparison results for $hitrtse \sim edc$
#| fig-width: 9
#| fig-height: 10

obj1 <- tidy_res_meffects(
  df = marginal_comparisons_1,
  sa_var = NULL,
  outcome = "hitrtse",
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj1)
```

```{r marginal-21}
#| label: fig-marginal-2-cortisolprod
#| fig-cap: Marginal comparison results for $cortisol production \sim edc$
#| fig-width: 9
#| fig-height: 10

obj2 <- tidy_res_meffects(
  df = marginal_comparisons_2,
  sa_var = NULL,
  outcome = "cortisol production",
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj2)
```

```{r marginal-22}
#| label: fig-marginal-2-cortisoneprod
#| fig-cap: Marginal comparison results for $cortisone production \sim edc$
#| fig-width: 9
#| fig-height: 10

obj2 <- tidy_res_meffects(
  df = marginal_comparisons_2,
  sa_var = NULL,
  outcome = "cortisone production",
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj2)
```

```{r marginal-23}
#| label: fig-marginal-2-corticosteroneprod
#| fig-cap: Marginal comparison results for $corticosterone production \sim edc$
#| fig-width: 9
#| fig-height: 10

obj2 <- tidy_res_meffects(
  df = marginal_comparisons_2,
  sa_var = NULL,
  outcome = "corticosterone production",
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj2)
```

```{r marginal-24}
#| label: fig-marginal-2-11b
#| fig-cap: Marginal comparison results for $11bhsd \sim edc$
#| fig-width: 9
#| fig-height: 10

obj2 <- tidy_res_meffects(
  df = marginal_comparisons_2,
  sa_var = NULL,
  outcome = "11bhsd",
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj2)
```

```{r marginal-3}
#| label: fig-marginal-3
#| fig-cap: Marginal comparison results for $hitrtse \sim metabolite$
#| fig-width: 9
#| fig-height: 5

obj3 <- tidy_res_meffects(
  df = marginal_comparisons_3,
  sa_var = NULL,
  outcome = "hitrtse",
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)
forest_plot(obj = obj3, r = 5)
```

### 2023-12-15 output/paper/_si.qmd
Merged tables and figures for marginal effects into forest plots.

tidy_res_meffects(
  df = marginal_comparisons_1SA,
  sa_var = "e3_sex",
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
Marginal comparison results for $hitrtse \sim edc \times sex$
:::

::: {#suppfig-marginal-2sa}
```{r marginal-2sa}
#| fig-width: 9
#| fig-height: 10

tidy_res_meffects(
  df = marginal_comparisons_2SA,
  sa_var = "e3_sex",
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
Marginal comparison results for $metabolite \sim edc \times sex$
:::

::: {#suppfig-marginal-3sa}
```{r marginal-3sa}
#| fig-width: 5
#| fig-height: 5

tidy_res_meffects(
  df = marginal_comparisons_3SA,
  sa_var = "e3_sex",
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
Marginal comparison results for $hitrtse \sim metabolite \times sex$
:::

>>>>

tidy_res_meffects(
  df = marginal_comparisons_1SA,
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
Marginal comparison results for $hitrtse \sim edc \times sex$
:::

::: {#suppfig-marginal-2sa}
```{r marginal-2sa}
#| fig-width: 9
#| fig-height: 12

tidy_res_meffects(
  df = marginal_comparisons_2SA |>
    tidylog::filter(
      !grepl("metabolism", outcome)
    ),
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
Marginal comparison results for $metabolite \sim edc \times sex$
:::

::: {#suppfig-marginal-3sa}
```{r marginal-3sa}
#| fig-width: 6
#| fig-height: 5

tidy_res_meffects(
  df = marginal_comparisons_3SA,
  sa_var = "e3_sex",
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$plot
```
Marginal comparison results for $hitrtse \sim metabolite \times sex$
:::

### 2023-12-15 output/paper/_tables.qmd
Merged tables and figures for marginal effects into forest plots.

```{r}
targets::tar_load(
  dplyr::matches("marginal_comparisons_(\\d)$"),
  store = store
)
```

```{r marginal-1}
#| label: tbl-marginal-1
#| tbl-cap: Marginal comparison results for $hitrtse \sim edc$

@@

```{r marginal-2}
#| label: tbl-marginal-2
#| tbl-cap: Marginal comparison results for $metabolite \sim edc$

@@

```{r marginal-3}
#| label: tbl-marginal-3
#| tbl-cap: Marginal comparison results for $hitrtse \sim metabolite$

@@

tidy_res_meffects(
  df = marginal_hypothesis_1SA,
  sa_var = "e3sex",
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```

@@

tidy_res_meffects(
  df = marginal_hypothesis_2SA,
  sa_var = "e3sex",
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```

@@

tidy_res_meffects(
  df = marginal_hypothesis_3SA,
  sa_var = "e3sex",
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```

>>>>

```{r}
#| eval: false
#| echo: false

targets::tar_load(
  dplyr::matches("marginal_comparisons_(\\d)$"),
  store = store
)
```

```{r marginal-1}
#| eval: false
#| echo: false
#| label: tbl-marginal-1
#| tbl-cap: Marginal comparison results for $hitrtse \sim edc$

@@

```{r marginal-2}
#| eval: false
#| echo: false
#| label: tbl-marginal-2
#| tbl-cap: Marginal comparison results for $metabolite \sim edc$

@@

```{r marginal-3}
#| eval: false
#| echo: false
#| label: tbl-marginal-3
#| tbl-cap: Marginal comparison results for $hitrtse \sim metabolite$

@@

tidy_res_meffects(
  df = marginal_hypothesis_1SA,
  sa_var = "e3sex",
  outcome = NULL,
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```

@@

tidy_res_meffects(
  df = marginal_hypothesis_2SA,
  sa_var = "e3sex",
  outcome = NULL,
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```

@@

tidy_res_meffects(
  df = marginal_hypothesis_3SA,
  sa_var = "e3sex",
  outcome = NULL,
  which_res = "hypothesis",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```
